

\begin{titlepage}
   % \centering
    \vspace*{1cm}
    
    {\Large \begin{center}
        \textbf{Acknowledgement}
    \end{center}} } \\[1.5cm]

% We are sincerely thankful to Dwarkadas J Sanghvi College of Engineering for providing
% us with the opportunity to conduct research on the project titled "Medchain"
% We express our gratitude and deepest appreciation to our mentor, Prof. Dipali Bhole, who has assisted us in conducting the research for this project and guided us through each stage.
We take this opportunity to express our deep sense of gratitude to our project guide Prof. Swapnil Gharat for his continuous guidance and encouragement throughout the duration of our project work. It is because of his experience and wonderful knowledge we were able to fulfil the requirement for the completion of this project within the stipulated time. We would also like to thank Dr. Narendra Shekokar, Vice Principal and Head of the Department Computer Science and Engineering (IoT and Cyber Security with Block Chain Technology) for his encouragement, whole-hearted cooperation and support.

We would also like to thank our Principal, Dr. Hari Vasudevan and the management of D.J. Sanghavi College of Engineering, Vile Parle (W), Mumbai for providing us with all the facilities and a work-friendly environment. We acknowledge by thanking the assistance provided by departmental staff, library, lab assistant lab attendants.
% We have learned extensively about different deep learning architectures, including DNNs, RNNs, and transformers, and their applications in cryptanalysis. This project has 
% deepened our understanding of both cryptographic vulnerabilities and the potential of 
% deep learning in identifying these weaknesses. We hope that this paper provides valuable 
% insights into the intersection of cryptanalysis and deep learning, contributing to the 
% ongoing discourse in cybersecurity. I would also like to thank all the project members.

\vspace{1cm}

\noindent
\textbf{Hiren Darji (60019230114)} \\
\textbf{Devarsh Chandiwade (60019230112)} \\
\textbf{Tushar Panchal  (60019230116)} \\
\textbf{Meenakshi Chandra (60019220126)} \\
